### 2021-07-01 paper.tex
edits on Sec.3

\def\Nequals#1{$\mathcal{N}{=}#1$}
\def\bZ{\mathbb{Z}}
\def\MF{\mathrm{MF}}
\def\TMF{\mathrm{TMF}}
\def\Tmf{\mathrm{Tmf}}
\def\tmf{\mathrm{tmf}}
\def\tr{\mathop{\mathrm{tr}}}

@@

\section{$\SL(2,\bZ_2)$ action and the anomalies}
\label{sec:sl2z}
In the last section we determined the 2-group structure of the $\so(2n_c)$ gauge theories with $2n_f$ flavors, by studying the group of the charges of line operators. 
In a QFT, any symmetry comes with its (possibly trivial) 't Hooft anomaly.
Here we determine the anomalies of these theories using the $\SL(2,\bZ_2)$ action on the set of QFTs with $\bZ_2$ 1-form symmetry.

@@

Let us say that  a four-dimensional spin QFT $Q$ with $\bZ_2$ 1-form symmetry is given.
We denote its partition function on a manifold $X$ by $Z_Q[E]$, 
where we suppress the dependence on $X$ in the notation and $E\in H^2(X;\bZ_2)$ is the background field for the $\bZ_2$ 1-form symmetry.
We then define $SQ$ and $TQ$ to be QFTs with partition functions given by the formula \begin{equation}
Z_{SQ}[B] \propto \sum_{E} (-1)^{\int_X B\cup E} Z_Q[E],\qquad
Z_{TQ}[E]= (-1)^{\int_X \tfrac12 \fP(E)} Z_Q[E].
\end{equation}
We can show that $S^2=T^2=1$ and $(ST)^3=1$, meaning that they generate $\SL(2,\bZ_2)$.
This operation was considered in  \cite{Gaiotto:2014kfa} as an analogue of the $\SL(2,\bZ)$ action on 3d theories with $\U(1)$ symmetry of  \cite{Witten:2003ya} and then further studied in \cite{Bhardwaj:2020ymp}.

Importantly, $\Spin(2n_c)$ and $\SO(2n_c)_\pm$  gauge theories with $2n_f$ flavors with the same $n_c$ and $n_f$ form a single orbit under this $\SL(2,\bZ)$ action.
More precisely, we need to make the distinction between $\Spin(2n_c)$ and $T(\Spin(2n_c))$ and  similarly between $\SO(2n_c)_\pm$ and $T(\SO(2n_c)_\pm)$, respectively.
Here the theories with $T$ prepended are different from the original ones only by its coupling to the background.
Then we have the following chain of actions: \begin{equation}
\begin{tikzpicture}
	\node at (0,0) {$
		T(\Spin) \stackrel{T}{\longleftrightarrow} 
		\Spin \stackrel{S}{\longleftrightarrow} 
		\SO_+ \stackrel{T}{\longleftrightarrow} 
		T(\SO_+) \stackrel{S}{\longleftrightarrow} 
		T(\SO_-) \stackrel{T}{\longleftrightarrow} 
		\SO_-.
	$};
	\draw[->] (-5,-1) -- (-5,-0.5);
	\draw[->] (5.4,-1) -- (5.4,-0.5);
	\draw (-5,-1) -- node[above] {\scriptsize $S$} (5.4,-1);
\end{tikzpicture}
\end{equation}

@@

The combined 1-form symmetry is either $\bZ_2\times \bZ_2$ or $\bZ_4$,
and we perform the $\SL(2,\bZ_2)$ action  by picking a $\bZ_2$ subgroup.
The symmetry and the anomaly of the resulting theory can be determined by a formal argument once those of the original theory 
and the action of the anomaly-free subgroup to be gauged are given \cite{Tachikawa:2017gyf}.

Let us work at the level of anomalies described at the level of cohomology, since we do not need to deal with anomalies more general than that.
We consider a $d$-dimensional QFT with a symmetry group $G$ with an anomaly specified by a cochain $\alpha\in C^{d+1}(G;\U(1))$. 
We pick a subgroup $H\subset G$ such that $\alpha$ trivializes in it, so that one can find $\mu \in C^d(H;\U(1))$ such that $\delta \mu = \alpha|_H$. 
We then gauge $H$, using $\mu$ as the action.
What determines the symmetry and the anomaly of the gauged theory is the data $(\mu,\alpha)$.
Clearly, given $\nu\in C^d(G;\U(1))$, the pair $(\mu,\alpha)$ and the pair $(\mu-\nu|_H,\alpha-\delta\nu)$ should give the same result, since we merely added the counterterm $\nu|_H$ as the action.
This allows us to always choose the pair of the form $(0,\alpha')$ equivalent to a given $(\mu,\alpha)$, 
by taking $\nu$ to be an arbitrary lift of $\mu$ from $H$ to $G$.
This is convenient in discussing the $\SL(2,\bZ_2)$ action,
since our $S$ operation is defined in the convention that $\mu=0$.

Now, what are the possible choices of $(\mu,\alpha)\sim(0,\alpha')$ we need to discuss?
Let us first consider $\bZ_2\times \bZ_2$ 1-form symmetry.
As detailed in the Appendix~\ref{sec:bordism}, the only possible anomaly for 4d spin QFTs with this symmetry is \begin{equation}
\alpha=2\pi i \cdot \frac12  B\beta E  \label{anom}
\end{equation} where $B,E\in H^2(Y;\bZ_2)$ are the background fields on the bulk 5d spin manifold $Y$.
Its restriction to $\bZ_2$ 1-form symmetry subgroup is trivial i.e. $\alpha|_{H=\bZ_2} = 0$,
and thus the possible choice of $\mu$ is simply the discrete theta angle \begin{equation}
\mu = 2\pi i \cdot \frac14 \fP(E).\label{P}
\end{equation}
This $\mu$ can be lifted from the $\bZ_2$ subgroup to the entire $\bZ_2\times \bZ_2$ group as a closed cochain.
Therefore, we only have to consider pairs $(0,0)$ and $(0,\alpha)$.

Next, we consider $\bZ_4$ 1-form symmetry.
Again in the Appendix~\ref{sec:bordism}, we show that this time there is no anomaly for $\bZ_4$ 1-form symmetry.
Therefore we can pick $\alpha=0$. Then the possible choice of $\mu$ for the $\bZ_2$ 1-form subgroup is again the discrete theta angle \eqref{P}.
One difference here is that the discrete theta angle \eqref{P} cannot be lifted as a closed cochain to the entire $\bZ_4$ 1-form subgroup.
As discussed in the Appendix~\ref{sec:nonclosedP}, with $\delta E=\beta a_2$,
where $a_2\in H^2(X;\bZ_4/\bZ_2)$,
one finds \begin{equation}
\alpha':=\delta \mu = 2\pi i \cdot \frac12 a_2 \beta_2 a_2.\label{anom'}
\end{equation}
Therefore, the pairs we need to consider are $(0,0)$ and $(\mu,0)\sim (0,\alpha')$.

@@

Let us now determine how the $\SL(2,\bZ_2)$ action affects these data.
The case `none' is very easy.
The additional $\bZ_2$ factor plays no role, and we find the chain of actions given by \begin{equation}
\begin{tikzpicture}
	\node at (0,0) {$
		\text{none} \stackrel{T}{\longleftrightarrow} 
		\text{none} \stackrel{S}{\longleftrightarrow} 
		\text{none} \stackrel{T}{\longleftrightarrow} 
		\text{none} \stackrel{S}{\longleftrightarrow} 
		\text{none} \stackrel{T}{\longleftrightarrow} 
		\text{none}.
	$};
	\draw[->] (-4.6,-1) -- (-4.6,-0.5);
	\draw[->] (4.5,-1) -- (4.5,-0.5);
	\draw (-4.6,-1) -- node[above] {\scriptsize $S$} (4.5,-1);
\end{tikzpicture}
\label{trivial-chain}
\end{equation}

@@

To make  the coupling \eqref{boo}  well-defined, we consider adding a background term to \eqref{boo} so that we have \begin{equation}
\exp\left[2\pi i\int_X \left( \frac14 \fP(E) +\frac12 B E + \frac14 \fP(B) \right)\right]
= 
\exp \left[2\pi i \int_X \frac14 \fP(E+B)\right] .
\end{equation}
This is perfectly well-defined and has no problem at all with the lifting,
if the newly-introduced background field $B$  also satisfies \begin{equation}
\delta B=\beta a_2.
\end{equation}
This means that, starting from `\Textended', performing $S$ and then $T$, we find a theory with the data `extended'.
Therefore, simply performing $S$ for the theory of the type `\Textended',  one  finds `\Textended'.

@@

\begin{table}
\centering
\[
\begin{array}{r@{\,}l|cccccc}
(n_c,&n_f)  & T(\Spin) & \Spin & \SO_+ & T(\SO_+) & T(\SO_-) & \SO_- \\
\hline
\vphantom{\Bigm|}(\text{even},&\text{even}) & \text{none}\tikzmark{a1}& \color{Purple}\text{none}\tikzmark{a2}& \text{none}\tikzmark{a3}& \tikzmark{a4}\text{none}& \tikzmark{a5}\text{none}& \tikzmark{a6}\text{none}\\
\vphantom{\Bigm|}(\text{odd},&\text{even}) & \text{\Textended}\tikzmark{b1} &\color{Purple}\text{extended}\tikzmark{b2} & \text{anomaly}\tikzmark{b3} & \tikzmark{b4}\text{anomaly} & \tikzmark{b5}\text{extended } & \tikzmark{b6}\text{\Textended} \\
\vphantom{\Bigm|}(\text{even},&\text{odd}) & \text{anomaly}\tikzmark{c1} & \color{Purple}\text{anomaly}\tikzmark{c2} & \text{extended}\tikzmark{c3} & \tikzmark{c4}\text{\Textended}  & \tikzmark{c5}\text{\Textended} & \tikzmark{c6}\text{extended} \\
\vphantom{\Bigm|}(\text{odd},&\text{odd}) & \text{extended}\tikzmark{d1} & \color{Purple}\text{\Textended}\tikzmark{d2} & \text{\Textended}\tikzmark{d3} & \tikzmark{d4}\text{extended}
 &  \tikzmark{d5}\text{anomaly} & \tikzmark{d6}\text{anomaly}   \end{array} 
\]
\tikz[overlay,remember picture]{%
\draw[<->,bend left,color=Orange,line width=1.5] (a1.north) to (a6.north);
\draw[<->,bend left,color=Orange,line width=1.5] (a2.north) to (a5.north);
\draw[<->,color=Orange,line width=1.5] (a3) to (a4);
\draw[<->,bend right,color=Orange,line width=1.5] (b1.south) to (b6.south);
\draw[<->,bend right,color=Orange,line width=1.5] (b2.south) to (b5.south);
\draw[<->,color=Orange,line width=1.5] (b3.south) to (b4.south);
\draw[<->,color=Orange,line width=1.5] (c1.south) to (d6.north);
\draw[<->,color=Orange,line width=1.5] (c2.south) to (d5.north);
\draw[<->,color=Orange,line width=1.5] (c3.south) to (d4.north);
\draw[<->,color=Orange,line width=1.5] (c4.south) to (d3.north);
\draw[<->,color=Orange,line width=1.5] (c5.south) to (d2.north);
\draw[<->,color=Orange,line width=1.5] (c6.south) to (d1.north);
}
\caption{The symmetry structure of $\so(2n_c)$ QCD with $2n_f$ flavors,
as deduced from the 2-group structures found in Sec.~\ref{sec:2-group}
and from the $\SL(2,\bZ_2)$ action discussed in this section.
The symmetry structure of the $\Spin$ case will be checked independently in the next section.
\label{table:refined}}
\end{table}

Comparing the chains of actions \eqref{trivial-chain} and \eqref{nontrivial-chain} we determined above 
and Table~\ref{table:2group},
we see that the anomaly is automatically determined and 
we obtain the result which was already presented in Table~\ref{table:main}.
More precisely, we should better distinguish $\Spin$ and $T(\Spin)$ etc.,
and we find the assignment given in Table~\ref{table:refined}.
As the way we determined the symmetry structures were somewhat indirect,
we confirm the symmetry structures of the $\Spin$ case in the next section
in a different means.

>>>>

\def\Nequals#1{$\mathcal{N}{=}#1$}
\def\bQ{\mathbb{Q}}
\def\bZ{\mathbb{Z}}
\def\MF{\mathrm{MF}}
\def\TMF{\mathrm{TMF}}
\def\Tmf{\mathrm{Tmf}}
\def\tmf{\mathrm{tmf}}
\def\tr{\mathop{\mathrm{tr}}}

@@

\section{$\SL(2,\bZ_2)$ action and the anomalies}
\label{sec:sl2z}
In the last section we determined the 2-group structure of the $\so(2n_c)$ gauge theories with $2n_f$ flavors, by studying the group of the charges of line operators. 
%In a QFT, any symmetry can come with an't Hooft anomaly.
Here we determine the anomalies of these symmetries, 
utilizing the $\SL(2,\bZ_2)$ action on the set of QFTs with $\bZ_2$ 1-form symmetry.

@@

Let us say that we are given a four-dimensional spin QFT $Q$ with $\bZ_2$ 1-form symmetry.
We denote its partition function on a manifold $X$ by $Z_Q[E]$, 
where we suppress the dependence on $X$ in the notation and $E\in H^2(X;\bZ_2)$ is the background field for the $\bZ_2$ 1-form symmetry.
We then define $SQ$ and $TQ$ to be QFTs with partition functions given by the formula \begin{equation}
Z_{SQ}[B] \propto \sum_{E} (-1)^{\int_X B\cup E} Z_Q[E],\qquad
Z_{TQ}[E]= (-1)^{\int_X \tfrac12 \fP(E)} Z_Q[E].
\end{equation}
We can show that $S^2=T^2=1$ and $(ST)^3=1$, meaning that they generate $\SL(2,\bZ_2)$.
This operation was introduced in  \cite{Gaiotto:2014kfa} as an analogue of the $\SL(2,\bZ)$ action on 3d theories with $\U(1)$ symmetry of  \cite{Witten:2003ya} and then further studied in \cite{Bhardwaj:2020ymp}.

Importantly, $\Spin(2n_c)$ and $\SO(2n_c)_\pm$  gauge theories with $2n_f$ flavors with the same $n_c$ and $n_f$ form a single orbit under this $\SL(2,\bZ)$ action.
More precisely, we need to make the distinction between $\Spin(2n_c)$ and $T(\Spin(2n_c))$ and  similarly between $\SO(2n_c)_\pm$ and $T(\SO(2n_c)_\pm)$, respectively.
Here the theories with $T$ prepended are different from the original ones only by its discrete theta coupling to the background.
Then we have the following chain of actions: \begin{equation}
\begin{tikzpicture}
	\node at (0,0) {$
		T(\Spin) \stackrel{T}{\longleftrightarrow} 
		\Spin \stackrel{S}{\longleftrightarrow} 
		\SO_+ \stackrel{T}{\longleftrightarrow} 
		T(\SO_+) \stackrel{S}{\longleftrightarrow} 
		T(\SO_-) \stackrel{T}{\longleftrightarrow} 
		\SO_-.
	$};
	\draw[->] (-5,-1) -- (-5,-0.5);
	\draw[->] (5.4,-1) -- (5.4,-0.5);
	\draw (-5,-1) -- node[above] {\scriptsize $S$} (5.4,-1);
\end{tikzpicture}
\label{sl2z-on-so}
\end{equation}

@@

The combined 1-form symmetry is either $\bZ_2\times \bZ_2$ or $\bZ_4$,
and we perform the $\SL(2,\bZ_2)$ action  by picking a $\bZ_2$ subgroup.
The symmetry and the anomaly of the resulting theory can be determined by a formal argument independent of the dynamics of the theory,
once the symmetry and the anomaly of the original theory 
and the action of the anomaly-free subgroup to be gauged are given, as discussed in \cite{Tachikawa:2017gyf}.

Let us work at the level of anomalies described by cohomology, since we do not need to deal with more general anomalies described by bordism.
We consider a $d$-dimensional QFT with a symmetry group $G$ with an anomaly specified by a cochain $\alpha\in C^{d+1}(G;\U(1))$. 
We pick a subgroup $H\subset G$ such that $\alpha$ trivializes in it, so that one can find $\mu \in C^d(H;\U(1))$ such that $\delta \mu = \alpha|_H$. 
We then gauge $H$, using $\mu$ as the action.
What determines the symmetry and the anomaly of the gauged theory is the data $(\mu,\alpha)$.
Clearly, given $\nu\in C^d(G;\U(1))$, the pair $(\mu,\alpha)$ and the pair $(\mu-\nu|_H,\alpha-\delta\nu)$ should give the same result, since we merely added the counterterm $\nu|_H$ as the action.
This allows us to always choose the pair of the form $(0,\alpha')$ equivalent to a given $(\mu,\alpha)$, 
by taking $\nu$ to be an arbitrary lift of $\mu$ from $H$ to $G$.\footnote{%
At this stage, the residual identifications $(0,\alpha')\sim (0,\alpha'')$ are of the form 
$\alpha''=\alpha'+\delta \nu$, where $\nu\in C^{d}(G;U(1))$ is required to satisfy $\nu|_H=0$.
Their equivalence classes form the relative cohomology group $H^{d+1}(G,H;U(1))$.
It might be interesting to study anomalies taking values in the relative cohomology groups.
}
This is convenient in discussing the $\SL(2,\bZ_2)$ action,
since our $S$ operation is defined in the convention that $\mu=0$.

\paragraph{The four choices:}
Now, what are the possible choices of $(\mu,\alpha)\sim(0,\alpha')$ we need to discuss?
Let us first consider $\bZ_2\times \bZ_2$ 1-form symmetry.
As detailed in the Appendix~\ref{sec:bordism}, the only possible anomaly for 4d spin QFTs with this symmetry is \begin{equation}
\alpha=%2\pi i \cdot 
\frac12  B\beta E  \label{anom}
\end{equation} where $B,E\in H^2(Y;\bZ_2)$ are the background fields on the bulk 5d spin manifold $Y$,
and we use $\bQ/\bZ$-valued cochains to describe the anomaly.
Its restriction to $\bZ_2$ 1-form symmetry subgroup is trivial i.e. $\alpha|_{H=\bZ_2} = 0$,
and thus the possible choice of $\mu$ is simply the discrete theta angle \begin{equation}
\mu =% 2\pi i \cdot
 \frac14 \fP(E),\label{P}
\end{equation}
where $\fP$ is the Pontrjagin square.
This $\mu$ can be lifted from the $\bZ_2$ subgroup to the entire $\bZ_2\times \bZ_2$ group as a closed cochain, 
and therefore does not affect the gauging process.
Therefore, we only have to consider pairs $(0,0)$ and $(0,\alpha)$.

Next, we consider $\bZ_4$ 1-form symmetry.
In the Appendix~\ref{sec:bordism}, we show that there is no anomaly for $\bZ_4$ 1-form symmetry.
Therefore we can pick $\alpha=0$. Then the only possible choice of $\mu$ for the $\bZ_2$ 1-form subgroup is again the discrete theta angle \eqref{P}.
One difference here is that the discrete theta angle \eqref{P} cannot be lifted as a closed cochain to the entire $\bZ_4$ 1-form subgroup.
As discussed in the Appendix~\ref{sec:nonclosedP}, with $\delta E=\beta a_2$,
where $a_2\in H^2(X;\bZ_4/\bZ_2)$,
one finds \begin{equation}
\alpha':=\delta \mu = %2\pi i \cdot 
\frac12 a_2 \beta_2 a_2,\label{anom'}
\end{equation}
where $\beta_2$ is the Bockstein associated to the sequence $0\to \bZ\to \bZ \to \bZ_4\to 0$,
whose action on $a_2$ can be defined since $a_2$ lifts to a $\bZ_4$-valued cochain.
Summarizing, the pairs  we need to consider for the $\bZ_4$ one-form symmetry are $(0,0)$ and $(\mu,0)\sim (0,\alpha')$.

@@

\paragraph{$\SL(2,\bZ_2)$ action on the four choices:}
Let us now determine how the $\SL(2,\bZ_2)$ action affects these data.
The case `none' is very easy.
The additional $\bZ_2$ factor plays no role, and we find the chain of actions given by \begin{equation}
\begin{tikzpicture}
	\node at (0,0) {$
		\text{none} \stackrel{T}{\longleftrightarrow} 
		\text{none} \stackrel{S}{\longleftrightarrow} 
		\text{none} \stackrel{T}{\longleftrightarrow} 
		\text{none} \stackrel{S}{\longleftrightarrow} 
		\text{none} \stackrel{T}{\longleftrightarrow} 
		\text{none}.
	$};
	\draw[->] (-4.6,-1) -- (-4.6,-0.5);
	\draw[->] (4.5,-1) -- (4.5,-0.5);
	\draw (-4.6,-1) -- node[above] {\scriptsize $S$} (4.5,-1);
\end{tikzpicture}
\label{trivial-chain}
\end{equation}

@@

To make  the coupling \eqref{boo}  well-defined, we consider adding a counterterm depending solely on the newly introduced field $B$ to \eqref{boo} so that we have \begin{equation}
\exp\left[2\pi i\int_X \left( \frac14 \fP(E) +\frac12 B E + \frac14 \fP(B) \right)\right]
= 
\exp \left[2\pi i \int_X \frac14 \fP(E+B)\right] .
\end{equation}
This is perfectly well-defined and has no problem at all with the lifting,
if the newly-introduced background field $B$  also satisfies \begin{equation}
\delta B=\beta a_2.
\end{equation}
This means that, starting from `\Textended', performing $S$ and then $T$, we find a theory with the data `extended'.
Therefore, simply performing $S$ for the theory of the type `\Textended',  one  finds `\Textended'.

@@

Let us now combine our result in Table~\ref{table:2group},
which summarizes our knowledge whether the 0-form part and the 1-form part form a nontrivial 2-group,
and the $SL(2,\bZ_2)$ action on the four choices, \eqref{trivial-chain} and \eqref{nontrivial-chain}, we determined above.
We first need to double each column of Table~\ref{table:2group},
since we need to distinguish $\Spin$ from $T\Spin$ and $\SO_\pm$ from $T\SO_\pm$.
The entry `product' in Table~\ref{table:2group} corresponds to either `none' or `anomaly',
and the entry `extended' there corresponds to either `extension' or `\Textended'.
We now demand that the $\SL(2,\bZ_2)$ action \eqref{sl2z-on-so} on $\so$ QCDT to be compatible with the $\SL(2,\bZ_2)$ action on the labels, \eqref{trivial-chain} and \eqref{nontrivial-chain}.
The only consistent assignment is given in Table~\ref{table:refined}.
As the way we determined the symmetry structures were somewhat indirect,
we confirm the symmetry structures of the $\Spin$ case in the next section
in a different means.

\begin{table}
\centering
\[
\begin{array}{r@{\,}l|cccccc}
(n_c,&n_f)  & T(\Spin) & \Spin & \SO_+ & T(\SO_+) & T(\SO_-) & \SO_- \\
\hline
\vphantom{\Bigm|}(\text{even},&\text{even}) & \text{none}\tikzmark{a1}& \color{Purple}\text{none}\tikzmark{a2}& \text{none}\tikzmark{a3}& \tikzmark{a4}\text{none}& \tikzmark{a5}\text{none}& \tikzmark{a6}\text{none}\\
\vphantom{\Bigm|}(\text{odd},&\text{even}) & \text{\Textended}\tikzmark{b1} &\color{Purple}\text{extended}\tikzmark{b2} & \text{anomaly}\tikzmark{b3} & \tikzmark{b4}\text{anomaly} & \tikzmark{b5}\text{extended } & \tikzmark{b6}\text{\Textended} \\
\vphantom{\Bigm|}(\text{even},&\text{odd}) & \text{anomaly}\tikzmark{c1} & \color{Purple}\text{anomaly}\tikzmark{c2} & \text{extended}\tikzmark{c3} & \tikzmark{c4}\text{\Textended}  & \tikzmark{c5}\text{\Textended} & \tikzmark{c6}\text{extended} \\
\vphantom{\Bigm|}(\text{odd},&\text{odd}) & \text{extended}\tikzmark{d1} & \color{Purple}\text{\Textended}\tikzmark{d2} & \text{\Textended}\tikzmark{d3} & \tikzmark{d4}\text{extended}
 &  \tikzmark{d5}\text{anomaly} & \tikzmark{d6}\text{anomaly}   \end{array} 
\]
\tikz[overlay,remember picture]{%
\draw[<->,bend left,color=Orange,line width=1.5] (a1.north) to (a6.north);
\draw[<->,bend left,color=Orange,line width=1.5] (a2.north) to (a5.north);
\draw[<->,bend left,color=Orange,line width=1.5] (a3.north) to (a4.north);
\draw[<->,color=Orange,line width=1.5] (b1.north) .. controls +(10:10em) ..  (b6.north);
\draw[<->,color=Orange,line width=1.5] (b2.north) .. controls +(10:5em) ..  (b5.north);
\draw[<->,color=Orange,line width=1.5] ([yshift=.2em]b3.west) to ([yshift=.2em]b4.east);
\draw[<->,color=Orange,line width=1.5] (c1.south) to (d6.north);
\draw[<->,color=Orange,line width=1.5] (c2.south) to (d5.north);
\draw[<->,color=Orange,line width=1.5] (c3.south) to (d4.north);
\draw[<->,color=Orange,line width=1.5] (c4.south) to (d3.north);
\draw[<->,color=Orange,line width=1.5] (c5.south) to (d2.north);
\draw[<->,color=Orange,line width=1.5] (c6.south) to (d1.north);
}
\caption{The symmetry structure of $\so(2n_c)$ QCD with $2n_f$ flavors,
as deduced from the 2-group structures found in Sec.~\ref{sec:2-group}
and from the $\SL(2,\bZ_2)$ action discussed in this section.
The symmetry structure of the $\Spin$ case will be checked independently in the next section.
\label{table:refined}}
\end{table}
